---
title: "Inferential Statistics Simulation"
author: "Victor Wildner"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Simulation Exercise

Overview: In a few (2-3) sentences explain what is going to be reported on.

## Setup

```{r}
library(tidyverse)
set.seed(144)
```

## Simulations
### Params
```{r}
n = 40
lambda = 0.2
simulations = 1000

matrix(rexp(n * simulations, lambda), simulations)
```




## Questions

Show the sample mean and compare it to the theoretical mean of the distribution.

Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

Show that the distribution is approximately normal.

## Simulations
Simulations: Include English explanations of the simulations you ran, with the accompanying R code. Your explanations should make clear what the R code accomplishes.

## Sample Mean x Theoretical Mean
Sample Mean versus Theoretical Mean: Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.

Sample Variance versus Theoretical Variance: Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

Distribution: Via figures and text, explain how one can tell the distribution is approximately normal.



